Identification of protoneutron star g-modes in gravitational-wave data

### 2020-06-03 introduction.tex
A bit of work in the introduction

>>>>

The computational modelling of the core-collapse escenario is challenging due the large number of physical processes involved whose role in the escenario is not completely understood. For instance, there are uncertainties in the stellar evolution of massive stars or in the nuclear and weak interactions necessary for the equation of state (EoS) or the neutrino interactions.  These large number of physical ingredients in addition to the necessary accuracy of the modelling of complex multidimensional interactions requires large computational resources. One simulation of one single progenitor in 3D with accurate neutrino transport and realistic equation of state (EoS) can take several months of intense calculations on a scientific supercomputer facility.
